fl0w 2.0 - a development environment for the\\ KIPR Wallaby

### 2017-03-22 paper.tex
Removed: disc0very; Added: References; General: Cleanup

\title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}
\author{\IEEEauthorblockN{Philip Trauner}
\IEEEauthorblockA{School of Computer Engineering\\
HTBLuVA Wiener Neustadt\\
Email: philip.trauner@arztpraxis.io}
\and
\IEEEauthorblockN{Christoph Heiss}
\IEEEauthorblockA{School of Computer Engineering\\
HTBLuVA Wiener Neustadt\\
Email: me@christoph-heiss.me}
\and
\IEEEauthorblockN{Sebastian Schaffler}
\IEEEauthorblockA{School of Computer Engineering\\
HTBLuVA Wiener Neustadt\\
Email: se.schaffler@gmail.com}}

\maketitle

@@

\subsubsection{Route}
A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call. \newpage

@@

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain sensor readouts as well as debug logs. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.

\subsubsection{Sensor readouts}

@@

\subsection{disc0very}
fl0w is using a client-server networking model but because of it's distributed nature the server is chosen randomly. This is implemented with UDP broadcasts that coordinate which controllers become clients and which controller becomes the server.

@@

>>>>

\title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}
\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss, Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann}
\IEEEauthorblockA{Department for Computer Science\\
Secondary Technical College\\
Wiener Neustadt, Austria\\
Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, krixizeh@gmail.com, sascha.zemann@gmail.com}
}
\maketitle

@@

\subsubsection{Route}
A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call.

@@

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain sensor readouts as well as debug logs. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.

@@

@@

\bibitem{Vue:Evan You}
Evan You, \emph{Vue.js}, \url{https://vuejs.org/},\\ product page,
accessed March 16th 2017
